The Probability of Convergent Evolution During Local Adaptation.

### 2014-07-03 patchy-selection-paper.tex
small changes throughout

\paragraph{Concluding thoughts}
The falling cost of population genomic sequencing means that we will soon have the
opportunity to study the interplay of adaptation with geography and ecology 
across many populations within a species. 
Our work suggests that even quite geographically close populations 
may be forced to adapt convergently when migration is geographically limited. 
Thus, systems where populations have been repeatedly subject to 
strong local selection pressures may offer the opportunity 
to study highly replicated convergent adaptation within a similar
genetic background \citep{Stern:13}.  
Such empricial work will also strongly inform our understanding of how gene flow 
may work to keep ecologically similar populations evolving in concert \citep{sexton2013genetic}.
Our results suggest that adaptation to shared environments is
certainly no guarantee of a shared genetic basis to adaptation, 
suggesting that rapid adaptation to a shared environment could potentially drive
speciation under some scenerios \citep[in a manner similar to ][]{}.

>>>>

\paragraph{Concluding thoughts}
The falling cost of population genomic sequencing means that we will soon have the
opportunity to study the interplay of adaptation with geography and ecology 
across many populations within a species. 
Our work suggests that even quite geographically close populations 
may be forced to adapt convergently when migration is geographically limited. 
Thus, systems where populations have been repeatedly subject to 
strong local selection pressures may offer the opportunity 
to study highly replicated convergent adaptation within a similar
genetic background \citep{Stern:13}.  
Such empricial work will also strongly inform our understanding of how gene flow 
may work to keep ecologically similar populations evolving in concert \citep{sexton2013genetic}.
Our results suggest that adaptation to shared environments is
certainly no guarantee of a shared genetic basis to adaptation, 
suggesting that rapid adaptation to a shared environment could potentially drive
speciation under some scenerios \citep[in a manner similar to ][]{Kondrashov:03}.
